%-------------------------
% Resume in Latex
% Author : Sachin Iyer
% Website: https://sachiniyer.com
% License : MIT
%------------------------

% Taken from template by Sourabh Bajaj

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item[]\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\certItem}[2]{
	\vspace{-1pt}\item[]
	\begin{tabular*}{0.96\textwidth}{l@{\extracolsep{\fill}}r}
		#1 & \textit{\small #2} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item[]
	\begin{tabular*}{0.96\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

 \newcommand{\resumeSubItem}[2]{
   \resumeItem{#1}{#2}\vspace{-4pt}
 }

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=1mm]}
		\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=3.75mm]}
		\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}

	\textbf{\href{https://sachiniyer.com/}{\Large Sachin Iyer}}
	&\href{https://sachiniyer.com/}{https://sachiniyer.com} \\
	\href{mailto:sachinjiyer@gmail.com}{sachinjiyer@gmail.com}
	& \href{https://github.com/sachiniyer}{https://github.com/sachiniyer}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://engineering.nyu.edu}{New York University}}{Brooklyn, NY}
{Bachelors of Science in Computer Science}{Exp. May. 2023}
\resumeSubheading
{\href{https://siliconvalley.basisindependent.com/}{Basis Independent Silicon Valley}}{San Jose, CA}
{High School Diploma}{Jul. 2020}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://www.amazon.jobs/en/teams/last-mile}{Amazon}}{Seattle, WA}
{Software Development Engineering Intern}{May 2022 -- August 2022}
\resumeItemListStart
\resumeItem{Data Aggregation Service}
{Created a full stack service to visualize last mile delivery data. Created a Typescript React frontend that calls an AWS API Gateway based backend implemented with Java Lambda Functions, API Gateway, S3, and Internal Amazon Services. Service sifts/caches through up to a TB of data per query with S3 Select.}
\resumeItem{Deployment/Observability Pipeline}
{The service is built with the AWS Typescript CDK. It is validated with unit and integration testing before being deployed through CodeDeploy and monitored with CloudWatch alarms and SNS.}
\resumeItemListEnd

\resumeSubheading
{\href{https://corelink.hpc.nyu.edu}{NYU Holodeck (Corelink)}}{Brooklyn, NY}
{Academic Researcher}{February 2021 -- Present}
\resumeItemListStart
\resumeItem{Framework Design}
{Designed a framework for developers to integrate their service with the Corelink network}
\resumeItem{\href{https://dev.hpc.nyu.edu/corelink/corelink-client/}{Client Development}}
{Developed and unified Corelink clients (Python, C++, Bash, Browser, and others)}
\resumeItem{\href{https://dev.hpc.nyu.edu/corelink/corelink-documentation/-/pipelines}{CI/CD}}
{Developed documentation, testing, and linting pipelines for the project in Gitlab}
\resumeItem{\href{https://vip.hsrn.nyu.edu/}{Mentorship}}
{Onboarded and managed 20+ members at Corelink. Created informational documentation and tutorials}
\resumeItem{\href{https://dev.hpc.nyu.edu/corelink/corelink-examples}{Audio Video Conferencing}}
{Created an audio/video service in C++ that interfaces with the Corelink network}
\resumeItemListEnd

\resumeSubheading
{\href{https://zkga.me}{Dark Forest}}{San Jose, CA}
{Graphics Intern}{December 2021 -- February 2022}
\resumeItemListStart
\resumeItem{\href{https://blog.zkga.me/renderer-plugin-contest}{Shader Development}}
{Implemented a typescript plugin that allows for custom shaders in the Dark Forest game.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.arubanetworks.com/company/about-us/}{Hewlett Packard Enterprise (Aruba Networks)}}{Santa Clara, CA}
{Cloud Intern}{June 2019 -- August 2019}
\resumeItemListStart
\resumeItem{Estimating Bandwidth}
{Estimated bandwidth using Auto ARIMA and other time series ML algorithms.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeItem{\href{https://github.com/sachiniyer/SynesthesiaVisualizer}{Synesthesia Visualizer}}
{Create a visualizer that mimics the experience of Auditory Visual Synthesis with librosa and yin. Utilizes AWS infrastructure (autoscaling ec2 cluster) for compute and WebGL for VR.}
\resumeItem{\href{https://github.com/sachiniyer/delivery-service}{Delivery Service}}
{Created a web crawling service to notify when there is a delivery slot available for Whole Foods, Costco, or Safeway. Used AWS SNS, ECS,  and Lambda functions. Created Docker containers with headless Chrome instances running Selenium.}
\resumeItem{\href{https://sachiniyer.com}{Personal Website}}
{Created a website that does real time 3D rendering in pure client side javascript with reactive interactive elements. Deployed with AWS CodeDeploy, API Gateway, CloudFront, IoT, S3, DynamoDB, and SNS.}
\resumeItem{\href{https://github.com/sachiniyer/ip-monitor}{IP Monitor}}
{Used the QT Framework and built a KDE widget to monitor public and private IP Addresses.}
\resumeItem{\href{https://github.com/sachiniyer/Electric-Trombone}{Electronic Trombone}}
{Engineer a midi controller in the form of a trombone using Arduino to apply standard instrument knowledge to electronic applications with capactive sensing and pid controllers.}
\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\resumeItem{Languages}
{Python, Typescript, Javascript/Node, C++, C, Rust, Java, (e)Lisp, Solidity, Shell Scripting, \LaTeX}
\resumeItem{Technologies}
{AWS, \href{https://github.com/sachiniyer/resume/tree/master/environment}{Linux}, Emacs, Docker/Kubernetes, ReactJS, Jupyter Notebooks, NGINX, \ldots}
\resumeSubHeadingListEnd


%--------Certifications------------
\section{Certifications}
\resumeSubHeadingListStart
\certItem{\href{https://www.credly.com/badges/ef46fdf4-2c55-474d-a963-9ee14107160f}{AWS Solutions Architect}}
{September 2021}
\certItem{\href{https://www.credly.com/badges/c8d7f47f-c6c1-4af9-8391-5b509b92b271}{AWS Cloud Practitioner}}
{August 2021}
\certItem{\href{https://coursera.org/share/29802cca497e8680b26b241d0ef50b59}{Stanford Machine Learning by Andrew Ng}}
{July 2020}
\certItem{\href{https://coursera.org/share/daef661212dab251985d69e4fb71f730}{AWS Fundamentals Specialization}}
{June 2020}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
